### 2016-11-18 intro.tex
Finished re-writing introduction

On April 26, 1920, Harlow Shapley and Heber Curtis took the stage at the
Smithsonian National Museum of History to debate each other on a topic of of
seemingly only academic interest: the nature of so-called ``Spiral Nebulae''.
The two eminent astronomers argued whether these nebulae were contained within
the Milky Way.  The implication if they lived within the Galaxy was that the
Galaxy was the Universe.  If they were not, the universe was far vaster than
many imagined.  This academic debate, like the Papal disagreement with Galileo
three hundred years earlier, was poised to reshape our understanding of the
vastness of the cosmos, and our insignificant place within it.

Today, nearly a century later, we no longer refer to these objects as ``Spiral
Nebulae'', but instead give them the name first reserved only for our own:
Galaxies.  Our Milky Way is but one of trillions of galaxies in the universe,
filling a volume that stretches out thousands of Megaparsecs in space and
billions of years in time.  These galaxies contain nearly all of the stars and
planets in the universe, much of the universe's gas, and are the places where
the former are constructed from the latter.

Galaxies within our universe are all made up of a common set of components.  The
most obvious component, and the one we can actually observe here in our own
galaxy with the naked eye, is the stellar component.  Galaxies are the sites in
which stars form, and those luminous stars are the most easily observed piece of
the galactic pie.  Those stars are formed out of a gaseous
interstellar medium (ISM).  This ISM is, in most galaxies, multiphase,
containing molecular gas, typically with densities $>100\;\rm{cm^{-3}}$ and
temperatures below $100\;\rm{K}$; a cold neutral medium with slightly higher
temperatures and lower densities; a warm neutral/ionized medium, with
temperatures around $10^4\;\rm{K}$; and a hot ionized medium with temperatures
$>10^5\;\rm{K}$.  All of this is surrounded by a hot ionized circumgalactic
medium that gives way to the hot coronal gas filling a dark matter halo much
larger than the galaxy disc itself.

Each of these baryonic components have been observed by a wide array of
telescopes both on earth and in orbit.  The dark matter that fills the galactic
halo must be observed indirectly: through the increased rotational velocity it
imparts on the stars and gas in the disc, and through gravitational lensing of
background objects.  While these observations are extremely powerful tools for
understanding how galaxies function in the present and how they have formed over
time, the immense timescales involved in both internal processes and in the
evolution of the galaxy itself make it impossible to watch them take place in
any single object.  To do this, and to test our theoretical models of how
galaxies evolve, requires numerical modeling.

Numerical modeling of galaxies is a difficult problem, as it involves processes
that take place over scales (both spatial and temporal) that span many orders of
magnitude.  This means that simulations will always be unable to resolve at
least some fraction of the physics taking place within the galaxy.  For this,
carefully designed ``sub-grid'' models are required to include the macroscopic
effects that unresolvable microscopic processes yield.  In this thesis, I
present a new sub-grid model for the feedback from massive stars (Chapter 2).  I
use that model to investigate how this feedback can regulate the formation of
stars within galaxies (Chapters 3 and 4), and finally show how this same
feedback is unneeded to produce galaxies that match the observations of
\citet{McGaugh2016} (Chapter 5).  I conclude with a summary of these results,
their implications, and some potential future directions for study in Chapter 6.

\section{The Cosmological Context of Galaxy Formation}
The modern picture of galaxy formation sits within the context of a $\Lambda$
Cold Dark Matter  ($\Lambda CDM$) cosmology.  This is a universe which has a no
curvature, the majority of its mass-energy in a cosmological constant $\Lambda$,
and most of its matter in a collisionless form (Dark matter).  Roughly $5\%$ of
the universe exists as baryons, which began as a mostly isothermal gas of
hydrogen and helium.  All of this began roughly $13.8$ billion years ago, with
the universe emerging from a state of infinite temperature and density,
expanding to form what we see today.  The primordial elemental abundances, with
$\sim4/5$ of the universe's baryons in hydrogen, and the remainder in helium,
was established just a few minutes after the big bang, during a brief period
called ``Big Bang Nucleosynthesis''.  The remaining elements of the periodic
table have been formed through stellar nucleosynthesis, through fusion in the
cores of stars and in energetic processes that take place during supernovae.

Much of what we know about the cosmology of our universe comes from observations
of the first light to escape the universe as it became optically thin and thus
transparent.  Prior to a redshift of $z=1100$, the universe had a high enough
ionization fraction that the mean free path for photons was short, making all of
space effectively opaque.  Once the universe became cool enough that hydrogen
became neutral, the optical depth was now low enough that photons could
free-stream, decoupled from baryons.  This ultraviolet light we observe today,
redshifted to microwaves with a temperature just $\sim2.7\;\rm{K}$.  When the
power spectrum of this radiation is measured, features in that spectrum can be
used to determine the components of the universe, as well as the spectrum of
density perturbations that will eventually form galaxies.

@@

The perturbation spectrum that forms the structure in which galaxies begins to
form is essentially a Gaussian random field, which \citet{Press1974} were able
to show produces a halo mass spectrum at a given time with a relatively simple form:
\begin{equation}
    \frac{dn}{dM}(M,t) =
    \sqrt{\frac{2}{\pi}}\frac{\rho_0\delta_c(t)}{M^2\sigma(M)} 
    \left\lvert\frac{d\ln{\sigma}}{d\ln{M}}\right\rvert
    \exp{\left[-\frac{\delta^2_c(t)}{2\sigma^2(M)}\right]}
\end{equation}
In this equation, $\rho_0$ is the mean density of the universe, and $\delta_c(t)$
is the critical overdensity for collapse at a given time $t$.  The mass variance
spectrum, $\sigma^2(M)$ can be determined observationally using the CMB power
spectrum.  This function gives a distribution of masses for the dark matter
halos that galaxies will begin to form within.  As these halos collapse,
gravitational torques from their surroundings will impart torques on them,
causing each galaxy to have angular momentum that will be conserved as their
baryonic components collapse and form a disc.

The collapse of baryons within the will depend strongly on whether the
post-virialized gas can cool radiatively.  As gas accretes onto a halo with
overdensity $\Delta$ it passes through a shock that raises its temperature to
the virial temperature:
\begin{equation}
    T_{virial} = \frac{2}{3}\frac{G\mu m_H}{k_B}\left({\frac{4\pi\rho_0\Delta
    M^2}{3}}\right)^{1/3}
\end{equation}
This means that more massive halos have larger virial temperatures, and,
depending on the mode of radiative cooling (atomic cooling from primordial
hydrogen, molecular hydrogen cooling, or cooling through metal lines), this may
give cooling times shorter than the current age of the universe.  These halos 
are the ones in which galaxy formation may begin, as their hot gaseous halos may
can collapse to form a disk, with a cold ISM where star formation can occur.

\begin{figure}
    \includegraphics[width=0.7\textwidth]{mass_function.eps}
    \caption[Galaxy mass function]{The observed mass function for galaxies in
    the nearby universe does not match the mass function for dark matter halos
    given in equation 1, scaled by the baryon fraction.  This tells us that
    there are additional physical processes involved in the formation of
    galaxies within their dark matter halos.  The most likely candidate for
    this is feedback from stars and black holes.  Of particular interest is the
    peak in star formation efficiency near $M_{200}=10^{12}M_\odot$.
    \textit{Image credit: Adapted from figure 1 in \citet{Ferrero2012}}}.
\end{figure}

This is of course all highly idealized, simple models for the earliest stages of
galaxy formation.  Each of these halos will begin to undergo mergers and
interactions with each other that can strip stars and gas through tidal and ram
pressure forces.  Inside each of these halos, the process of disc collapse, star
formation, and feedback from those stars involves the complex interplay of
radiation, hydrodynamics, magnetic fields, and gravity on length scales as much
as $10^{11}$ times smaller than the virial radius.  None of this physics is
simple enough to be captured by these sorts of analytic models, and so numerical
simulations have become a keystone for galaxy formation research.

@@

Modern galaxy simulations do far more than merely integrate the equations of
motion for a few hundred test particles in a gravitational field.  Today, state
of the art simulations will track gravity (including self-gravity) for stars,
gas, and dark matter; evolve Euler's equations for the hydrodynamics of gaseous
baryons; include models for radiative cooling of gas that allow for cooling from
both hydrogen and metal lines; form stars from dense gas; and include models for
feedback from massive stars and black holes.  Often, simulations will also
include treatments for radiative transfer and magneto-hydrodynamics as well.
Hydrodynamical solvers usually come in one of two classes: Eulerian or
Lagrangian.  Eulerian methods discretize space, breaking a simulation volume
into a grid of cells that each contains a number of scalar and vector quantities
that are advected according to the solver scheme.  Lagrangian methods instead
discretize mass, breaking the gaseous volume into discrete points, each of which
is moved to advect the quantities it contains, with smoothing functions used to
interpolate values in between particles.  Recently, new methods have begin to
hybridize features of each of these classes as well. Gravity is typically solved
using algorithms designed to minimize the workload that would be needed for a
direct summation of each particle or grid cell ($\mathcal{O}(N^2)$ for N grid
cells/particles).  Most codes use a tree-like or spectral algorithm to reduce
the cost to $\mathcal{O}(N\log{N})$, though a handful are beginning to adopt the
even faster Fast Multipole Method to reduce gravity calculation cost to
$\mathcal{O}(N)$.

In simulations of galaxies, the formation and deaths of individual stars are
typically unresolvable (in fact, this is currently true even for simulations of
molecular clouds).  This means that the formation of stars must be handled by
sub-grid approximations of the complex physics taking place at the sites of star
formation.  The simplest and most straight forward model is to simply assume
that gas will form stars at some fraction of the local free-fall time.  This leads
to a star formation rate that scales like $\dot \rho_* = c_* \rho_{gas}^{1/2}$,
where the single parameter $c_*$ is intended to capture the unresolved
efficiency of star formation at small scales.

@@

\section{The Importance of Feedback}
Simple analytic models for galaxy formation began with a universal picture of
their formation:  density perturbations that, over time, collapse under their
own self-gravity.  It is tempting to assume that this process dominates at all
scales of interest, as clearly stars form through the gravitational collapse of
gas clouds within the ISM (which themselves may form through their own
self-gravity).  This leads to a catastrophe at nearly all scales.  If gravity
is unopposed in star and galaxy formation, the timescales involved would scale
like the freefall time:
\begin{equation}
    t_{ff} = \sqrt{3\pi/32G\rho}
\end{equation}
The observed timescales for star and galaxy formation are much longer than this.
For galaxies, this predicts a complete conversion of gas to stars in $t_{ff} <<
t_{Hubble}$, which would mean the universe today would contain far more stars
than it does, and no actively star-forming galaxies.

We now know that galaxy and star formation is not a one
way process of gravitational collapse.  A number of internal processes
(``feedback'') within galaxies can liberate energy greater than the
gravitational binding energy of molecular clouds (and indeed even comparable to
the binding energy of the entire halo).  Early simulations that omitted
these feedback processes found that gas rapidly collapsed into the smallest
halos at high redshift, wildly overproducing stars in small galaxies at
high redshift (the ``cooling catastrophe'').  Galaxies like our own develop
unrealistically compact morphologies.  Simulations of individual molecular
clouds develop star formation rates an order of magnitude too high.  Aside from
establishing a number of observed galaxy properties, there are a observations of
feedback processes taking place.  Fast, massive outflows have been observed
leaving the discs of starburst galaxies and quasar host galaxies.  These
outflows must be powered by feedback.

@@

Feedback energy may come from a number of sources.  The two primary sources are
massive stars and supermassive black holes (SMBHs).  Massive stars ($M>5M_\odot$)
live short, violent lives.  During their lives, they will drive fast
$v>1000\;\rm{km/s}$ stellar winds, and heat their surrounding gas with UV
radiation.  At the end of their lives $4-30\;\rm{Myr}$ later, these stars die in
extremely energetic core-collapse supernovae, liberating $\sim10^{51}\;\rm{erg}$.
This energy imparts heat and momentum to the surrounding ISM, and can accelerate
cosmic rays in the shocks that are driven.  In galaxies with actively growing
SMBHs, the accretion disc that forms as gas funnels into the black hole can
reach temperatures exceeding $10^9\;\rm{K}$ through viscous heating.  This
makes these accretion discs some of the most luminous objects in the universe,
and can heat the gas that surrounds the galaxy to choke off the accretion of new
material to form stars.

@@

The greatest difficulty with including the effects of feedback in simulations of
galaxy evolution is the combination of extreme energy gradients in a relatively
small mass/volume.  Without overwhelmingly high resolution, hot feedback gas
will be numerically mixed with cold ISM, often resulting in gas with
temperatures of $\sim10^5\;\rm{K}$, at the peak of the ISM cooling curve where
cooling times are extremely short.  This results in feedback energy being
completely lost due to radiative cooling.  Indeed, as \citet{Thacker2000}
showed, how feedback energy is deposited into the ISM has a huge impact on
whether that feedback has any impact.  This problem has been tackled using a few
different strategies.  Since overcooling is the problem, many models have
attacked this directly by either temporarily disabling cooling
\citep{Stinson2006} or depositing feedback energy into a second, nonthermal
energy component \citep{Agertz2013}.  While this does limit radiative losses, it
produces gas that exists in an unphysical region of the $\rho-T$ phase diagram,
which may not have the correct entropy to escape buoyantly.  It also has the
potential to introduce an \textit{undercooling} problem as resolution becomes
higher and feedback-heated gas becomes resolvable.  Alternatively, energy may be
injected not as heat, but as momentum, which naturally does not cool.
Unfortunately, this adds the additional complexity of momentum cancellation (how
to treat neighbouring stars/clusters?), and if this momentum results in strong
shocks, these shocks will convert the momentum right back into thermal energy
that can radiate away the feedback energy the model is designed to preserve.
This often means kinetic/momentum feedback models must be combined with
hydrodynamic decoupling that renders feedback-heated gas into a form that does
not interact with the surrounding ISM.  Naturally, this makes outflow properties
strongly influenced by numerical choices.

A third choice is to stochastically deposit feedback energy only when enough
energy is available to raise gas temperatures high enough for cooling times to
be short \citep{DallaVecchia2012,Crain2015}.  In these models, supernovae events
are effectively grouped together, somewhat decoupling feedback from star
formation.  The choice of temperature to heat gas to is a purely numerical
parameter, and can dramatically change the effectiveness of these models.
Finally, some \citep{Springel2010} attempt to directly address the unphysical
numerical mixing of hot and cold gas by separating the two phases and tracking
each component separately.  This completely solves the overcooling problem, and
allows the two components to cool radiatively.   Unfortunately, it also means
that cold star-forming gas is permanently coupled to hot feedback-heated gas:
effectively making the ISM an anchor holding down potential hot outflows.  This
means these multiphase models have to be coupled with parameterized models to
capture outflows.  Often, these simple models simply choose a fraction of
feedback energy to be deposited as kinetic ``kicks'' to a some gas particles.
Like other kinetic feedback models, this is frequently combined with
hydrodynamical decouplings.

@@

\section{Superbubble Feedback}
The formation of massive stars takes place mostly in clusters of $10^4$ or more
stars.  This means that the supernovae of these stars can be treated not as
individual dumps of $10^{51}\;\rm{erg/SN}$, but instead as a luminosity of
$10^{38}\;\rm{\frac{erg}{s \cdot M_\odot}}$.  This allows us to use stellar wind
models like \citet{Weaver1977} to study the evolution of superbubbles driven by
clustered supernovae.  Each individual supernovae's eject thermalizes in a small
region within the center of the bubble, and the resulting hot gas drives a shock
that sweeps up the surrounding ISM.  In a short time, the swept-up ISM can
efficiently radiatively cool, resulting in a thin, cold shell surrounding a hot
bubble.

@@

Chapter 4 extends the results presented in chapter 3 by simulating an additional
17 cosmological galaxies, reproducing the full sample presented in
\citet{Stinson2010} with updated hydrodynamics and the new feebdack model
described in chapter 2.  This sample spans the peak of the star formation
efficiency found by abundance matching studies like \citet{Moster2013}, and
using it we are able to show that supernovae feedback is unable to regulate
galaxies more massive than the peak halo mass of $10^{12}\;M_\odot$.  By
analyzing the outflow properties of these galaxies, we are able to determine a
global relation between the halo mass (or disc mass) and the outflow mass
loadings.  We show that the decreasing efficiency of SN-driven winds is an
inevitable consequence of the energy budget available from SN alone.

@@

Finally, in chapter 6 we conclude with a discussion of how each of these results
together improve our understanding of supernovae-regulated star formation
in the formation of disc galaxies.  We discuss how the results presented here
fit in with past research and the with the current direction of research in
galaxy evolution theory.  We conclude with a discussion of the future directions
that this research points, and a number of open questions related to it that I
hope to answer in the coming years.

>>>>

\section{The Cosmological Context of Galaxy Formation}
The modern picture of galaxy formation sits within the context of a $\Lambda$
Cold Dark Matter  ($\Lambda CDM$) cosmology \citet{White1978,Mo1998}.  This is a
universe which has a no curvature ($\Omega = 1$), and today has the majority of
its mass-energy in a cosmological constant $\Lambda$ ($\Omega_\Lambda \sim
0.7$), and most of its matter in a collisionless form (Dark matter) ($\Omega_m
\sim 0.3$) \citep{Planck2014}.  Roughly $5\%$ of the universe exists as baryons ($\Omega_b \sim
0.05$), which began as a mostly isothermal gas of hydrogen and helium.  All of
this began roughly $13.8$ billion years ago, with the universe emerging from a
state of infinite temperature and density, expanding to form what we see today.
The primordial elemental abundances, with $\sim4/5$ of the universe's baryons in
hydrogen, and the remainder in helium, was established just a few minutes after
the big bang, during a brief period of ``Big Bang Nucleosynthesis''
\citep{Alpher1948}.  The remaining elements of the periodic table have been
formed through stellar nucleosynthesis, through fusion in the cores of stars and
in energetic processes that take place during supernovae (SN)\citet{Wagoner1967}.

Much of what we know about the cosmology of our universe comes from observations
of the first light to escape the universe as it became optically thin: the
cosmic microwave background (CMB).  Prior to a redshift of $z=1100$, the
universe had a high ionization fraction such that the mean free path for
photons was short, making all of space effectively opaque.  Once the universe
became cool enough that hydrogen became neutral, the optical depth was now low
enough that photons could free-stream, decoupled from baryons.  This ultraviolet
light we observe today, redshifted to microwaves with a temperature just
$\sim2.7\;\rm{K}$.  When the power spectrum of this radiation is measured,
features in that spectrum can be used to determine the components of the
universe, as well as the spectrum of density perturbations that will eventually
form galaxies.

@@

The perturbation spectrum that forms the structure in which galaxies begins to
form is essentially a Gaussian random field, which \citet{Press1974} were able
to show produces a halo mass spectrum at a given time with a relatively simple form:
\begin{equation}
    \frac{dn}{dM}(M,t) =
    \sqrt{\frac{2}{\pi}}\frac{\rho_0\delta_c(t)}{M^2\sigma(M)} 
    \left\lvert\frac{d\ln{\sigma}}{d\ln{M}}\right\rvert
    \exp{\left[-\frac{\delta^2_c(t)}{2\sigma^2(M)}\right]}
\end{equation}
In this equation, $\rho_0$ is the mean density of the universe, and
$\delta_c(t)$ is the critical overdensity for collapse at a given time $t$.  The
mass variance spectrum, $\sigma^2(M)$ can be determined observationally using
the CMB power spectrum \citep{Planck2015}.  This function gives a distribution
of masses for the dark matter halos that galaxies will begin to form within.  As
these halos collapse, gravitational torques from their surroundings will impart
torques on them \citep{Barnes1987}, causing galaxies to have a distribution of angular momenta.
High resolution N-body simulations have found that dark matter halos have both a
universal density profile \citep{Navarro1996,Merritt2006} as well as a universal
angular momentum profile \citep{Bullock2001}.

The collapse of baryons within the will depend strongly on whether the
post-virialized gas can cool radiatively \citep{Rees1977}.  As gas accretes onto
a halo with overdensity $\Delta$ it passes through a shock that raises its
temperature to the virial temperature:
\begin{equation}
    T_{virial} = \frac{2}{3}\frac{G\mu m_H}{k_B}\left({\frac{4\pi\rho_0\Delta
    M^2}{3}}\right)^{1/3}
\end{equation}
This means that more massive halos have larger virial temperatures, and,
depending on the mode of radiative cooling (atomic cooling from primordial
hydrogen, molecular hydrogen cooling, or cooling through metal lines), this may
give cooling times shorter than the current age of the universe.  These halos 
are the ones in which galaxy formation may begin, as their hot gaseous halos may
can collapse to form a disk, with a cold ISM where star formation can occur.

As gas does begin to cool within these halos, it will lose pressure support (by
radiating away thermal energy), but {\it not} angular momentum.  This means that
the baryons, which typically carry the same specific angular momentum as the
halo itself, will flatten to form an exponential disc as they cool
\citep{Fall1980,Mo1998}.  Within this disc, an interstellar medium (ISM) will form.  This
ISM is multiphase, containing both hot ($T\sim10^5\;\rm{K}$) and cold
($T\sim10-100\;\rm{K}$) in quasistatic equilibrium \citep{McKee1977}.
\begin{figure}
    \includegraphics[width=0.7\textwidth]{mass_function.eps}
    \caption[Galaxy mass function]{The observed mass function for galaxies in
    the nearby universe does not match the mass function for dark matter halos
    given in equation 1, scaled by the baryon fraction.  This tells us that
    there are additional physical processes involved in the formation of
    galaxies within their dark matter halos.  The most likely candidate for
    this is feedback from stars and black holes.  Of particular interest is the
    peak in star formation efficiency near $M_{200}=10^{12}M_\odot$.
    \textit{Image credit: Adapted from figure 1 in \citet{Ferrero2012}}}.
\end{figure}

This is of course all highly idealized, simple models for the earliest stages
and broadest strokes of galaxy formation.  Each of these halos will begin to
undergo mergers and interactions with each other that can strip stars and gas
through tidal and ram pressure forces.  Inside each of these halos, the process
of disc collapse, the formation of a multiphase ISM, star
formation, and feedback from those stars involves the complex, nonlinear
interplay of radiation, hydrodynamics, magnetic fields, and gravity on length
scales as much as $10^{11}$ times smaller than the virial radius.  None of this
physics is simple enough to be captured by these sorts of analytic models, and
so numerical simulations have become a keystone for galaxy formation research.

Numerical modeling of galaxies is a difficult problem, as it involves processes
that take place over scales (both spatial and temporal) that span many orders of
magnitude.  This means that simulations will always be unable to resolve at
least some fraction of the physics taking place within the galaxy.  For this,
carefully designed ``sub-grid'' models are required to include the macroscopic
effects that unresolvable microscopic processes yield.

@@

Modern galaxy simulations do far more than merely integrate the equations of
motion for a few hundred test particles in a gravitational field.  Today, state
of the art simulations will track gravity (including self-gravity) for stars,
gas, and dark matter; evolve Euler's equations for the hydrodynamics of gaseous
baryons; include models for radiative cooling of gas that allow for cooling from
both hydrogen and metal lines; form stars from dense gas; and include models for
feedback from massive stars and black holes.  Often, simulations will also
include treatments for radiative transfer and magneto-hydrodynamics as well.

Gravity is typically solved using algorithms designed to minimize the workload
that would be needed for a direct summation of each particle or grid cell
($\mathcal{O}(N^2)$ for N grid cells/particles).  This becomes intractable for
larger numbers of resolution elements, as the workload will scale as the sixth
power of the linear resolution (an order of magnitude better linear resolution
will be $10^6$ times more expensive!).  In order to reduce these costs,
algorithms have been developed that allow for more efficient gravitational
force calculations.  Tree-based methods \citep{Barnes1986} reduce the
computational cost of long-ranged (and thus less significant) force
calculations by using space-partitioning trees.  Short-range force calculations
are done particle-by-particle, while long-range forces are calculated against
larger tree cells, thus reducing the cost of calculating gravity to
$\mathcal{O}(N\log N)$.  Particle-Particle/Particle-Mesh ($P^3M$) methods
\citep{Couchman1991} take a produce similar scalings, but rather than using a
spatial tree rely on a spectral Fourier-based approach to calculate long-ranged
interactions.  Recently, the Fast Multipole Method \citep{Greengard1987} has
been adapted for calculation of gravitational forces
\citep{Dehnen2002,Hahn2013} using a multipole expansion of Green's functions.
This allows for extremely efficient gravity calculation, scaling linearly with
particle number ($\mathcal{O}(N)$).

Hydrodynamical solvers usually come in one of two classes: Eulerian or
Lagrangian.  Eulerian methods discretize space, breaking a simulation volume
into a grid of cells that each contains a number of scalar and vector
quantities that are advected according to the solver scheme.  Eulerian schemes
typically allow for higher-order solvers, lower intrinsic noise, and better
resolved discontinuities \citep{Teyssier2002,Stone2008,Bryan2014}.  They suffer
from intrinsic mixing and diffusion that scales with the flow velocity relative
to the grid \citet{Agertz2007,Tasker2008}.  Lagrangian methods instead
discretize mass, breaking the gaseous volume into discrete points, each of
which is moved to advect the quantities it contains, with smoothing functions
used to interpolate values in between particles.  Lagrangian methods couple
easily to tree codes for gravity calculation, are Galilean invariant, and
intrinsically conserve mass, energy, and momentum (linear and angular)
\citep{Katz1996,Wadsley2004,Springel2005}.  They require the use of artificial
viscosity to handle shocks, and as such have difficulty in capturing subsonic
turbulence \citep{Bauer2012}. Recently, new methods have begin to hybridize
features of each of these classes as well \citep{Springel2010,Hopkins2015}.

@@

The earliest attempt to track the formation of a galaxy in a cosmological
context with the effects of star formation and feedback included was by
\citep{Katz1992}.  This simulation used the Lagrangian TREESPH method
\citep{Hernquist1989} to evolve a parcel of gas and dark matter from an initial
linear perturbation, including small-scale power derived from CDM predictions.
Gas was allowed to cool radiatively using rates calculated for primordial gas.
This study introduced a model for star formation that is still the standard for
most simulations of galaxy formation.  Observations \citep{Schmidt1959} have
suggested that the star formation rate is a power law of the gas density:
$\dot\rho_*\propto\rho_{gas}^\alpha$, with $\alpha=1-2$.  If it is assumed that
gas collapses to form stars in some multiple $c_*$ of its freefall time,
$t_{ff}$, a simple star formation model can be built with the form:
\begin{equation}
    \dot\rho_* = \frac{c_*\rho_{gas}}{t_{ff}} = c_*\sqrt{\frac{\rho^3_{gas}}{4\pi G}}
\end{equation}
\citet{Katz1992} used a $c_*$ parameter of $0.1$, which is within the range of
what is typically used in simulations today ($1-100\%$).  On top of the model
for star formation, feedback was included without the use of any significant
subgrid model:  $10^{51}\;\rm{erg/SN}$ worth of energy was injected back into
the ISM.  One of the key findings of \citet{Katz1992} was that the vast majority
of SN energy was radiated away, making them very ineffective at regulating star
formation within the galaxy.  In the end, they find that the peak starformation
in the simulated galaxy was nearly 10 times greater than in present day
galaxies.  \citet{Thacker2000} later showed that the smoothing of energy used by
\citet{Katz1992} resulted in a large overestimation of the cooling rates in
feedback-heated gas. Since this study, much work has gone into developing models
for SN feedback that address the issue of overcooling that was present in these
earlier simulations.

\section{The Importance of Feedback}
We now know that galaxy and star formation is not a one way process of
gravitational collapse.  A number of internal processes (``feedback'') within
galaxies can liberate energy greater than the gravitational binding energy of
molecular clouds (and indeed even comparable to the binding energy of the entire
halo).  Analytic calculations that omit feedback processes found that gas should
rapidly collapse into the smallest halos at high redshift, wildy overproducing
stars in small galaxies at high redshift (the ``cooling catastrophe'')
\citep{Cole2001,Benson2003}.  Galaxies like our own develop unrealistically
compact morphologies without feedback \citet{Stinson2006}.  Simulations of
individual molecular clouds develop star formation rates an order of magnitude
too high \citep{Agertz2013}.  Aside from regulating star formation and the
growth of galaxies, there are a observations of the large-scale impact of
feedback. Lyman $\alpha$ forest observations probing the intergalactic medium
(IGM) have found that the IGM is polluted with metal ions at great distances
from any galaxies \citep{Sargent1988,Songaila1996,Dave1998}.  These metals must have
been ejected by galactic outflows from the discs of galaxies where they formed.
These fast, massive outflows have been observed leaving the discs of
starburst galaxies and quasar host galaxies \citep{Veilleux2005,Werk2014}.
These outflows must be powered by feedback.

@@

Feedback energy may come from a number of sources.  The two primary sources are
massive stars and supermassive black holes (SMBHs).  Massive stars
($M>5M_\odot$) live short, violent lives.  During their lives, they will drive
fast $v>1000\;\rm{km/s}$ stellar winds, and heat their surrounding gas with UV
radiation.  At the end of their lives $4-30\;\rm{Myr}$ later, these stars die
in extremely energetic core-collapse SN, liberating
$\sim10^{51}\;\rm{erg}$.  Figure 1.3 shows the total budget of available energy
liberated by a population of stars.  This energy imparts heat and momentum to
the surrounding ISM, and can accelerate cosmic rays in the shocks that result
\citep{Bell1978}.  In galaxies with actively growing SMBHs, the accretion disc
that forms as gas funnels into the black hole can reach temperatures exceeding
$10^9\;\rm{K}$ through viscous heating.  This makes these accretion discs some
of the most luminous objects in the universe, and can heat the gas that
surrounds the galaxy to choke off the accretion of new material to form stars.

\begin{figure}
    \includegraphics[width=0.8\textwidth]{FB_budget.ps}
    \caption[Stellar feedback energy budget]{The energy released by a population
    of stars with solar metallicity is $\sim 2\times10^{51}\;\rm{erg/M_\odot}$.
    Most of this energy is released as photons, over the lifetime of each star.
    These will couple poorly to the surrounding ISM, and so have little impact
    on disrupting all but the densest gas.  While stellar winds typically have
    comparable luminosity to supernovae, they occur for an order of
    magnitude less time ($\sim4$ Myr vs. $\sim40$ Myr).  This means that
    supernovae, despite only contributing $\sim1\%$ of the total energy released
    by a stellar population, may have the greatest impact.  The data shown here was
    produced with {\sc starburst99} \citep{Leitherer1999}}
\end{figure}

@@

The greatest difficulty with including the effects of feedback in simulations of
galaxy evolution is the combination of extreme energy gradients in a relatively
small mass/volume.  Without overwhelmingly high resolution, hot feedback gas
will be numerically mixed with cold ISM, often resulting in gas with
temperatures of $\sim10^5\;\rm{K}$, at the peak of the ISM cooling curve where
cooling times are extremely short.  This results in feedback energy being
completely lost due to radiative cooling, as was first seen by \citet{Katz1992}.
Indeed, as \citet{Thacker2000} showed, how feedback energy is deposited into the
ISM has a huge impact on whether that feedback has any impact.  This problem has
been tackled using a few different strategies.

Since overcooling is the problem, many models have attacked this directly by
either temporarily disabling cooling \citep{Thacker2000,Stinson2006} or
depositing feedback energy into a second, nonthermal energy component
\citep{Agertz2013}.  While this does limit radiative losses, it produces gas
that exists in an unphysical region of the $\rho-T$ phase diagram, which may not
have the correct entropy to escape buoyantly.  It also has the potential to
introduce an \textit{undercooling} problem as resolution becomes higher and
feedback-heated gas becomes resolvable.  Alternatively, energy may be injected
not as heat, but as momentum, which naturally does not cool
\citep{Scannapieco2006,DallaVecchia2008,Dubois2008}.  Unfortunately, this adds
the additional complexity of momentum cancellation (how to treat neighbouring
stars/clusters?), and if this momentum results in strong shocks, these shocks
will convert the momentum right back into thermal energy that can radiate away
the feedback energy the model is designed to preserve \citep{Durier2012}.  This
often means kinetic/momentum feedback models must be combined with hydrodynamic
decoupling that renders feedback-heated gas into a form that does not interact
with the surrounding ISM \citep{Springel2003,Vogelsberger2013}.  Naturally, this
makes outflow properties strongly influenced by numerical choices
\citet{DallaVecchia2008}.  A third choice is to stochastically deposit feedback
energy only when enough energy is available to raise gas temperatures high
enough for cooling times to be short \citep{DallaVecchia2012,Crain2015}.  In
these models, SN events are effectively grouped together, somewhat
decoupling feedback from star formation.  The choice of temperature to heat gas
to is a purely numerical parameter, and can dramatically change the
effectiveness of these models.  Finally, some \citep{Springel2003,Murante2015}
attempt to directly address the unphysical numerical mixing of hot and cold gas
by separating the two phases and tracking each component separately.  This
completely solves the overcooling problem, and allows the two components to cool
radiatively.   Unfortunately, it also means that cold star-forming gas is
permanently coupled to hot feedback-heated gas: effectively making the ISM an
anchor holding down potential hot outflows.  This means these multiphase models
have to be coupled with parameterized models to capture outflows.  Often, these
simple models simply choose a fraction of feedback energy to be deposited as
kinetic ``kicks'' to a some gas particles.  Like other kinetic feedback models,
this is frequently combined with hydrodynamical decouplings.

@@

The formation of massive stars takes place mostly in clusters of $10^4$ or more
stars.  This means that the SN of these stars can be treated not as
individual dumps of $10^{51}\;\rm{erg/SN}$, but instead as a luminosity of
$10^{38}\;\rm{\frac{erg}{s \cdot M_\odot}}$.  This allows us to use stellar wind
models like \citet{Weaver1977} to study the evolution of superbubbles driven by
clustered SN.  Each individual SN's eject thermalizes in a small
region within the center of the bubble, and the resulting hot gas drives a shock
that sweeps up the surrounding ISM.  In a short time, the swept-up ISM can
efficiently radiatively cool, resulting in a thin, cold shell surrounding a hot
bubble.

@@

Chapter 4 extends the results presented in chapter 3 by simulating an additional
17 cosmological galaxies, reproducing the full sample presented in
\citet{Stinson2010} with updated hydrodynamics and the new feedback model
described in chapter 2.  This sample spans the peak of the star formation
efficiency found by abundance matching studies like \citet{Moster2013}, and
using it we are able to show that SN feedback is unable to regulate
galaxies more massive than the peak halo mass of $10^{12}\;M_\odot$.  By
analyzing the outflow properties of these galaxies, we are able to determine a
global relation between the halo mass (or disc mass) and the outflow mass
loadings.  We show that the decreasing efficiency of SN-driven winds is an
inevitable consequence of the energy budget available from SN alone.

@@

Finally, in chapter 6 we conclude with a discussion of how each of these results
together improve our understanding of SN-regulated star formation
in the formation of disc galaxies.  We discuss how the results presented here
fit in with past research and the with the current direction of research in
galaxy evolution theory.  We conclude with a discussion of the future directions
that this research points, and a number of open questions related to it that I
hope to answer in the coming years.
